%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------
\cventry
{University of Edinburgh} % Organization
{Research assistant} % Job title
{Edinburgh, Scotland} % Location
{April 2021 - September 2021} % Date(s)
{ % Description(s) of tasks/responsibilities
    \begin{cvitems}
        \item {
            Developing a Carpentries-style course in high-dimensional statistics.
        }
        \item {
            Certification as a trained Carpentries instructor (April 2021).
        }
    \end{cvitems}
}

\cventry
{Fios Genomics} % Organization
{Bioinformatician} % Job title
{Edinburgh, Scotland} % Location
{October 2015 - August 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
    \begin{cvitems}
        \item {
            Communicating regularly with clients to plan projects and explain 
            results.
        }
        \item {
            Exploratory and statistical analysis for academics and commercial 
            clients.
        }
        \item {
            Statistical analysis \& visualisations for client publications \& 
            commercial research projects.
        }
        \item {Extensive software development.}
        \item {Author \& maintainer of several proprietary R packages.}
        \item {System administration tasks (VMware, Ansible).}
    \end{cvitems}
}

\cventry
{Queen's University Belfast} % Organization
{IT Support} % Job title
{Belfast, Northern Ireland} % Location
{September 2014 - September 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
    \begin{cvitems}
        \item {Technical support, maintenance, document recovery, device configuration.}
    \end{cvitems}
}

\cventry
{IT Support} % Job title
{Kelly Services} % Organization
{Galway, Ireland} % Location
{April 2014 - September 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
    \begin{cvitems}
        \item {Technical support for major online game: troubleshooting, management, configuration.}
        \item {Friendly, professional, clear, and informed communication at all times.}
    \end{cvitems}
}

\cventry
{Research Assistant} % Job title
{Irish Marine Institute} % Organization
{Galway, Ireland} % Location
{April 2011 - September 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
    \begin{cvitems}
        \item {Extracting marine specimens, chromatography, bioassays, devising procedures \& SOPs.}
        \item {Deep sea research cruise on Celtic Explorer (primary Irish research vessel), interdisciplinary team of 20. Sample classification and cataloguing, communication and co-ordination with other researchers.}
    \end{cvitems}
}


\end{cventries}
